Geometric models overestimate lake depth due to imperfect slope measurement

### 2020-11-28 manuscript/agujournaltemplate.tex
note distance upper bound phenomena

Although proxy distance to lake center was often much larger in magnitude compared to the true distance to the deepest point of lakes’, they were strongly related ($R^2$ = 0.8). In contrast, proxy nearshore land slope and true in-lake slope were more weakly related ($R^2$ = 0.17). For slope measures, most lakes had lower magnitude (i.e. shallower) nearshore land slope compared to true in-lake slope (Figure \ref{fig2}). Taken together, these results suggest that proxy distance to the center of lakes is representative of true distance to the deepest point of lakes whereas proxy nearshore land slope is not representative of true in-lake slope. The strong relationship between distance to the center of lakes and distance to the deepest point means that it is possible to compute a "correction factor" to convert between the two measures (See best-fit equations in Figure \ref{fig2}).

>>>>

Although proxy distance to lake center was often larger in magnitude compared to the true distance to the deepest point of lakes’, they were strongly related ($R^2$ = 0.8). Note that the coefficient of determination for this relationship is not strictly correct given that distance to lake center is an upper bound on distance to the deepest point of lakes. In contrast to distance metrics, proxy nearshore land slope and true in-lake slope were more weakly related ($R^2$ = 0.17). For slope measures, most lakes had lower magnitude (i.e. shallower) nearshore land slope compared to true in-lake slope (Figure \ref{fig2}). Taken together, these results suggest that proxy distance to the center of lakes is representative of true distance to the deepest point of lakes whereas proxy nearshore land slope is not representative of true in-lake slope. The strong relationship between distance to the center of lakes and distance to the deepest point means that it is possible to compute a "correction factor" to convert between the two measures (See best-fit equations in Figure \ref{fig2}).
